Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-01-07 manuscript/draft_rsfmri.Rmd
add figures and QA measures (pre-christmas commit possibly not ready)

# load packages
library(car) # version 3.0.9
library(plyr) # version 1.8.6
library(dplyr) # version 1.0.2
library(tidyr) # version 1.1.2
library(kableExtra) # version 1.2.1
library(ggplot2) # version 3.3.2
library(patchwork) # version 1.0.1; API for sequentially building up a plot (similar to gridExtra and cowplot)
library(cowplot)
library(RColorBrewer) # version 1.1.2
library(psych) # version 2.0.8
#library(lsr)
#library(wesanderson) # colour palette
#library(haven)

library(lme4)
library(sjPlot)

library(knitr) # version 1.30
```

```{r "knit setup", include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex") 
options(knitr.kable.NA = '') # hide NA in tables
# set working directory of knit (RMarkdown) to directory of Rproj
opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
setwd(knitr::opts_knit$get("root.dir"))
```

@@

```
<!-- STUDY PROCEDURE --> Subjects arrived in the morning (between 07:00 and 12:00) after an overnight fast. They underwent medical assessments including an interview, blood draw and anthropometric measurements before having a one our break for <!-- standadized??  -->breakfast. MRI scanning was done after further psychological tests (for details see @Prehn_2020).
```{r figBMIdescr, fig.align='center', out.width="90%", fig.cap="BMI over time.", echo=FALSE}
# eval = TRUE, fig.asp = 0.7, fig.width = 6
source("report/figures.R")
figBMIdescr <- mk_figBMIdescr(final)

@@

# Results

## Quality control
We performed different quality controls for the rsfMRI data.
As described in @Beyer_2020, there was a significant interaction of group and time on mFD. In particular, the intervention group reduced in head motion in the follow-up assessments compared to the control group.
We also inspected DVARS, a measurement of whole-brain variation in signal which is often reflective of noise in the data. We saw that DVARS did not qualitatively differ between groups and time points, and that the correlation of DVARS and mFD remained similar over time points.
This indicates that even though there was a decrease in head motion in the intervention versus control group, the impact of head motion on imaging data remained similar over the study period.
```{r tableQA, fig.cap="Summary table of QA measures"}

for (i in 1:nrow(final)) {
  tmp = strsplit(toString(final[i, "scan_dir"]), '/')[[1]][8]
  conf = read.csv(
    paste0("/data/pt_02161/preprocessed/resting/detailedQA/metrics/",
      tmp, "/confounds.csv"))
  tmp = cor.test(conf$DVARS, conf$FD)
  final[i, "corr_DVARS_FD"] = tmp$estimate
  final[i, "mean_DVARS"] = mean(conf$DVARS, na.rm = TRUE)
  final[i, "max_DVARS"] = max(conf$DVARS, na.rm = TRUE)
  final
}

```{r figDvarsmFD, fig.align = "center", out.width="100%", fig.cap='Summary of quality measures DVARS and mFD'}
# ,  fig.align='center', }
# eval = TRUE, fig.asp = 0.7, fig.width = 6

@@

```{r FDFC correlation, eval=FALSE, echo=FALSE}
source("/data/pt_02161/Analysis/Preprocessing/qa/rs_qa/group_level_QA/QC_FC_correlations/calc_qc_fc_correlations.R")

FDFC=calc_qc_fc(final)
write.csv(FDFC,"./report/FDFCcorrelations.csv", row.names = FALSE)
```

```{r tableQcfc, echo=FALSE}
res <- read.csv("./report/FDFCcorrelations.csv")
rownames(res) <- c("minimally processed", "AROMA", "AROMA + CC", "AROMA + CC + GSR")
colnames(res) <- c('mean FD-QC', 'median FD-QC', 'sig. vertex', 'sig. vertex BH', 'distance-FD-QC', 'pval')

tab_qc_fc <- mk_tableQcfc(res)
tab_qc_fc
```

Further, we evaluated the impact of our denoising pipelines. Table \@ref(tab:tableQcfc) shows that in the minimally preprocessed data, mFD and connectivity was significantly positively correlated (mean Spearman's $r = $`r round(res[1,1],2)`), with a strong distance dependence (mean Spearman's $r = $`r round(res[1,5],2)`).  Denoising procedures (AROMA, AROMA+CC, AROMA+CC+GSR) gradually reduced the correlation of mFD and connectivity, and also alleviated the distance dependency. AROMA+CC+GSR performed best, with almost no mFD-FC correlation (mean Spearman's $r = $`r round(res[4,1],2)`), and minimal positive distance dependence (mean Spearman's $r = $`r round(res[4,5],2)`). Yet, AROMA+CC also performed well, and we thus calculated our analysis models for both preprocessing schemes.

@@

#### with adjustment for age, sex, meanFD
<!-- Brain mask: Group*Time Interaction [CORRECTED] -->
There was no interaction of group and time point regarding the resting state connectivity for neither the PCC nor the NAcc as was hypothesized. Nor was there a significant main effect for any of the covariates of interest (time, group) in clusterwise inference with FWE correction.

#### with adjustment for age and sex
Similarly, there were only non-findings when reducing the number of nuisance covariates by leaving out mean FD. Results did not differ between analyses of connetivity maps from different preprocessing pipelines.
<!-- There was no other significant co-activation for any other region of interest for neither of the preprocessing variants. -->

@@

## Interaction effect group by time on aggregated FC (preregistered analysis)

### DMN for two timepoints
```{r calc DMN two tp, eval = FALSE, echo = FALSE}
R1 = lme4::lmer(DMN_FC ~ timepoint*group + (1|subj))
R0 = lme4::lmer(DMN_FC ~ timepoint + group + (1|subj))
```
### DMN for two timepoints, adjusted for age, sex, mean FD
```{r calc DMN two tp adjusted, eval = FALSE, echo = FALSE}
R1 = lme4::lmer(DMN_FC~ timepoint*group + age + sex + meanFD (1|subj))
R0 = lme4::lmer(DMN_FC ~ timepoint + group + age + sex + meanFD (1|subj))
```
### DMN for three timepoints, adjusted for age, sex, mean FD
```{r calc DMN three tp, eval = FALSE, echo = FALSE}
R1 = lme4::lmer(DMN_FC~ timepoint*group + age + sex + meanFD (1|subj))
R0 = lme4::lmer(DMN_FC ~ timepoint + group + age + sex + meanFD (1|subj))
```

### reward
```{r calc rew two tp, eval = FALSE, echo = FALSE}
R1 = lme4::lmer(rew_FC ~ timepoint*group + (1|subj))
R0 = lme4::lmer(rew_FC ~ timepoint + group + (1|subj))
```
### reward for two timepoints, adjusted for age, sex, mean FD
```{r calc rew two tp adjusted, eval = FALSE, echo = FALSE}
R1 = lme4::lmer(DMN_FC ~ timepoint*group + age + sex + meanFD (1|subj))
R0 = lme4::lmer(DMN_FC ~ timepoint + group + age + sex + meanFD(1|subj))
```
### reward for three timepoints, adjusted for age, sex, mean FD
```{r calc rew three tp, eval = FALSE, echo = FALSE}
R1 = lmer(DMN_FC ~ timepoint*group + age + sex + meanFD (1|subj))
R0 = lmer(DMN_FC ~ timepoint + group + age + sex + meanFD (1|subj))
```

>>>>

# load packages
library(car) # version 3.0.9
library(plyr) # version 1.8.6
library(dplyr) # version 1.0.2
library(tidyr) # version 1.1.2
library(kableExtra) # version 1.2.1
library(ggplot2) # version 3.3.2
library(patchwork) # version 1.0.1; API for sequentially building up a plot (similar to gridExtra and cowplot)
library(cowplot)
library(RColorBrewer) # version 1.1.2
library(psych) # version 2.0.8

#library(lsr)
library(wesanderson) # colour palette
#library(haven)

library(lme4)

library(sjPlot) #only works for HTML output
library(texreg) #works for Rmarkdown
library(knitr) # version 1.30
```

```{r "knit setup", include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE) # fig.height=2, fig.width=4)
options(knitr.table.format = "latex") 
options(knitr.kable.NA = '') # hide NA in tables
# set working directory of knit (RMarkdown) to directory of Rproj
opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
setwd(knitr::opts_knit$get("root.dir"))
```
\newpage
# Abstract

\newpage
# Introduction

@@

```
<!-- STUDY PROCEDURE --> Subjects arrived in the morning (between 07:00 and 12:00) after an overnight fast. They underwent medical assessments including an interview, blood draw and anthropometric measurements before having a one our break for <!-- standadized??  -->breakfast. MRI scanning was done after further psychological tests (for details see @Prehn_2020).
```{r figBMIdescr, fig.align='center', out.width="90%", fig.cap="BMI over time.", echo=FALSE}
# eval = TRUE, fig.asp = 0.7, fig.width = 6
source("report/figures.R")
figBMIdescr <- mk_figBMIdescr(final)
figBMIdescr
```

@@

\newpage
# Results

## Quality control
We performed different quality controls for the rsfMRI data.
As described in @Beyer_2020, group and time show an interaction effect for mFD where the intervention group reduced in head motion in the follow-up assessments compared to the control group.
We also inspected DVARS, a measure of whole-brain signal variation which is reflective of noise in the data. We saw that DVARS did not qualitatively differ between groups and time points, and that the correlation of DVARS and mFD remained similar over time points.
This indicates that even though there was a decrease in head motion in the intervention versus control group, the impact of head motion on imaging data remained similar over the study period.
```{r tableQcfc, echo=FALSE}
res <- read.csv("./report/FDFCcorrelations.csv")
rownames(res) <- c("minimally processed", "AROMA", "AROMA + CC", "AROMA + CC + GSR")
colnames(res) <- c('mean FD-QC', 'median FD-QC', 'sig. vertex', 'sig. vertex BH', 'distance-FD-QC', 'pval')

tab_qc_fc <- mk_tableQcfc(res)
tab_qc_fc
```
Further, we evaluated the impact of our denoising pipelines on different quality metrics following [@Ciric_2018]. Table \@ref(tab:tableQcfc) shows that in the minimally preprocessed data, mFD and FC between nodes was significantly positively correlated (mean Spearman's r = `r round(res[1,1],2)`). This relationship was negatively associated with distance between nodes (mean Spearman's r = `r round(res[1,5],2)`).  
Denoising procedures (AROMA, AROMA+CC, AROMA+CC+GSR) gradually reduced the correlation of mFD and connectivity, and reduced the distance dependency. Contrary to previous reports, GSR did not exercabate mFD-FC distance dependency. Overall, AROMA+CC+GSR performed best, with almost no mFD-FC correlation (mean Spearman's r = `r round(res[4,1],2)`), and minimal positive distance dependence (mean Spearman's r = `r round(res[4,5],2)`). Yet, AROMA+CC also performed well, and we thus calculated our analysis models for both preprocessing schemes.

```{r calculate summary of QA, eval=FALSE, echo=FALSE}
for (i in 1:nrow(final)) {
  tmp = strsplit(toString(final[i, "scan_dir"]), '/')[[1]][8]
  conf = read.csv(
    paste0("/data/pt_02161/preprocessed/resting/detailedQA/metrics/",
      tmp, "/confounds.csv"))
  tmp = cor.test(conf$DVARS, conf$FD)
  final[i, "corr_DVARS_FD"] = tmp$estimate
  final[i, "mean_DVARS"] = mean(conf$DVARS, na.rm = TRUE)
  final[i, "max_DVARS"] = max(conf$DVARS, na.rm = TRUE)
  final
}
```

```{r figDvarsmFD, fig.align = "center", out.width="100%", fig.cap='Summary of quality measures DVARS and mFD', echo=FALSE}
final=read.csv(file = "./report/all_QA_measures.csv")

@@

```{r FDFC correlation, eval=FALSE, echo=FALSE}
source("/data/pt_02161/Analysis/Preprocessing/qa/rs_qa/group_level_QA/QC_FC_correlations/calc_qc_fc_correlations.R")
FDFC=calc_qc_fc(final)
write.csv(FDFC,"./report/FDFCcorrelations.csv", row.names = FALSE)
```

```{r figNetworks, echo=FALSE, out.width="49%", out.height="30%", fig.cap="Resting state networks based on AROMA+CC+GSR input data, one-sample t-tests adjusting for age and sex over all timepoints and participants with bootstrapped clusterwise inference (p FWE<0.05)", fig.subcap=c("DMN seeded from precuneus", "Reward network seeded from Nucleus Accumbens"),fig.show='hold',fig.align='center'}
networks=c("../report/DMN_thresholded_for_clusterFWE005.png","../report/Rew_thresholded_for_clusterFWE005.png")
knitr::include_graphics(networks)
```

Figure \@ref{fig:figNetworks} shows the DMN and reward network which we used for extracting the aggregated FC values. Both networks included the typically described brain regions (i.e. medial prefrontal cortex, parietal lobules and posterior hippocampus for the DMN, and anterior cingulare, right amygdala and ventromedial-prefrontal cortex for the reward network).

```{r prepare tsnr ROI plot, echo=FALSE}
final$subj.ID_tp=paste0(final$subj.ID,'_', final$tp)

tsnr=read.table("/data/pt_02161/Analysis/Preprocessing/qa/rs_qa/group_level_QA/check_tsnr/tsnr_in_ROIs.txt")
tsnr=tsnr[tsnr$V1!="subj",]
colnames(tsnr)=c("subj.ID_tp","roi","median","mean","sd")
levels(tsnr$roi)=droplevels(tsnr$roi)
levels(tsnr$roi)=c("NAcc", "precuneus")
tsnr$mean=as.double(tsnr$mean)

final_tsnr=merge(final, tsnr, by="subj.ID_tp", all.x=TRUE)

p<-ggplot(aes(as.factor(roi), mean),data=final_tsnr) +
  geom_violin(aes(fill=roi)) + geom_jitter(height = 0, width = 0.1) + xlab("Region of interest") + ylab("average tSNR") + 
  scale_fill_manual(values=wes_palette("Darjeeling2",4,type="discrete")[2:3]) +
  theme(axis.text=element_text(size=10),
  axis.title=element_text(size=12),
  strip.text = element_text(size=12),
  legend.position="")
```

```{r figtSNR,fig.cap="Lower tSNR in the region of interest NAcc versus precuneus used for seed-based connectivity (shown are all 101 timepoints)", out.width="60%",  echo=FALSE}
p
```
Yet, the reward network was less pronounced (overall lower T-values) and symmetric (no significant connectivity with left amygdala), which might be due to lower SNR in the seeded brain region (see Figure \@ref{fig:figtSNR}.

@@

#### with adjustment for age, sex, meanFD
<!-- Brain mask: Group*Time Interaction [CORRECTED] -->
There was no interaction of group and time point regarding the resting state connectivity for neither the PCC nor the NAcc seeds against our initial hypothesis. There also was no significant main effect for any of the covariates of interest (time, group) in clusterwise inference with FWE correction.

#### with adjustment for age and sex
Similarly, there were no significant clusters when leaving out mean FD. Results did not differ between AROMA+CC and AROMA+CC+GSR preprocessing pipelines.
<!-- There was no other significant co-activation for any other region of interest for neither of the preprocessing variants. -->

<!-- Neurovault -->
Unthresholded maps for the t-tests of the DMN and reward network (which were used for data aggregation) as well as contrasts of group, time and group-by-time interaction are on [NeuroVault](insert link here).

@@

## Interaction effect group by time on aggregated FC (preregistered analysis)
```{r load agg FC data and prepare, echo=FALSE}
agg_FC_DMN=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/DMN/agg_FC_DMN.txt")
agg_FC_DMN_ID=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/DMN/agg_FC_DMN_ID.txt")
agg_FC_Rew_ID=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/Rew/agg_FC_Rew_ID.txt")
agg_FC_Rew=read.table("/data/pt_02161/Results/Project2_resting_state/connectivity/Analysis/aggFC/Rew/agg_FC_Rew.txt")
for (i in c(1:nrow(agg_FC_DMN_ID))){
  agg_FC_Rew[i,"subj.ID_tp"]=strsplit(base::strsplit(as.character(agg_FC_Rew_ID[i,"V1"]),'/')[[1]][10],'_nacc')[[1]][1]
  agg_FC_DMN[i,"subj.ID_tp"]=strsplit(base::strsplit(as.character(agg_FC_DMN_ID[i,"V1"]),'/')[[1]][10],'_pcc')[[1]][1]
}

colnames(agg_FC_Rew)=c("mean_Rew_conn","sd_Rew_conn","subj.ID_tp")
colnames(agg_FC_DMN)=c("mean_DMN_conn","sd_DMN_conn","subj.ID_tp")

final_FC=merge(final, agg_FC_Rew, by="subj.ID_tp", all.x=TRUE)
final_FC=merge(final_FC, agg_FC_DMN, by="subj.ID_tp", all.x=TRUE)
final_FC$subj.ID=as.factor(final_FC$subj.ID)

#calculate mean FD over timepoints
final_FC.meanFD=tapply(X=final_FC$logmFD,
                        INDEX=final_FC$subj.ID, FUN=mean, na.rm=TRUE)
final_FC$mean.logmFD=
  final_FC.meanFD[as.numeric(final_FC$subj.ID)]
final_FC$within.logmFD=
  final_FC$logmFD-final_FC$mean.logmFD
```

### DMN for two timepoints
```{r vif for models, echo=FALSE}
test_vif=lm(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex + mean.logmFD, data=final_FC)
vif_res=vif(test_vif)
```

```{r calc DMN two tp,results = 'asis', echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvDMN2tp=anova(R1,R0)
```

```{r DMN2tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), custom.model.names = c("R0", "R1"), float.pos = "h",  custom.coef.names=c("Intercept (BL, NBARS)", "Timepoint FU", "Group BARS", "Timepoint x Group"),  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```

### DMN for two timepoints, adjusted for age, sex, mean FD
```{r calc DMN two tp adjusted, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + logmFD +(1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex + logmFD +(1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvDMN2tpadj=anova(R1,R0)
res=summary(R1)
#tab_model(R0,R1)
```

```{r DMN2tpadj results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), reorder.coef=c(1, 2, 3, 7, 4, 5, 6),custom.coef.names=c("Intercept (BL, NBARS)","Timepoint FU", "Group BARS", "Age", "Sex","mean FD","Timepoint x Group"), custom.model.names = c("R0", "R1"), float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```

### DMN for three timepoints, adjusted for age, sex, mean FD
```{r calc DMN three tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD +(1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +(1|subj.ID), data=final_FC)
anvDMN3tp=anova(R1,R0)
```

```{r DMN3tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), reorder.coef=c(1, 2, 3, 4, 8,9,5,6,7),custom.coef.names=c("Intercept (BL, NBARS)", "Timepoint FU", "Timepoint FU2", "Group BARS", "Age", "Sex","mean FD","Timepoint FU x Group", "Timepoint FU2 x Group"), custom.model.names = c("R0", "R1"), float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```

```{r DMN conn over three timepoints, echo=FALSE}
fig_DMNconn<-mk_figDMNdescr(final_FC)
fig_DMNconn
```

### Reward network for two time points
```{r calc rew two tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tp=anova(R1,R0)
```

```{r Rew2tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), custom.coef.names=c("Intercept (BL, NBARS)","Timepoint FU", "Group BARS", "Timepoint x Group"), custom.model.names = c("R0", "R1"), float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```

### Reward network for two timepoints, adjusted for age, sex, mean FD
```{r calc rew two tp adjusted, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + logmFD +(1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +logmFD +(1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tpadj=anova(R1,R0)
```
```{r Rew2tpadj results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), reorder.coef=c(1, 2, 3, 7, 4, 5, 6),custom.coef.names=c("Intercept (BL, NBARS)","Timepoint FU", "Group BARS", "Age", "Sex","mean FD","Timepoint x Group"), custom.model.names = c("R0", "R1"), float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```

### Reward network for three timepoints, adjusted for age, sex, mean FD
```{r calc rew three tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + logmFD +(1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +logmFD +(1|subj.ID), data=final_FC)
anvRew3tp=anova(R1,R0)
```
```{r Rew3tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(list(R0,R1), reorder.coef=c(1, 2, 3, 4, 8,9,5,6,7),custom.coef.names=c("Intercept (BL, NBARS)", "Timepoint FU", "Timepoint FU2", "Group BARS", "Age", "Sex","mean FD","Timepoint FU x Group", "Timepoint FU2 x Group"), custom.model.names = c("R0", "R1"), float.pos = "h",  center = TRUE, digits = 3, leading.zero = FALSE, single.row = TRUE, include.adjrs = FALSE, include.bic = FALSE, table = FALSE, use.packages = FALSE)
```
```{r Rew conn over three timepoints, echo=FALSE}
fig_Rewconn<-mk_figRewdescr(final_FC)
fig_Rewconn
```
